\chapter{Files From Directory {\textit{nc\_test4}}}

\section{h5testszip.c}

***PASS

\section{Test cdm\_sea\_soundings.c}

ESDM does not support compound datatypes from NetCDF!

Sorry! Unexpected result, ../../nc\_test4/cdm\_sea\_soundings.c, line: 60

\section{Test test\_szip.c}

ESDM does not support compression from NetCDF!

Sorry! Unexpected result, ../../nc\_test4/test\_szip.c, line: 72

\section{Test tst\_atts1.c}

Sorry! Unexpected result, ../../nc\_test4/tst\_atts1.c, line: 205

\section{Test tst\_atts2.c}

ESDM does not support compound datatypes from NetCDF!

Sorry! Unexpected result, ../../nc\_test4/tst\_atts2.c, line: 73

\section{Test tst\_atts3.c}

Sorry! Unexpected result, ../../nc\_test4/tst\_atts3.c, line: 2396

\section{Test tst\_atts.c}

Sorry! Unexpected result, ../../nc\_test4/tst\_atts.c, line: 91

\section{Test tst\_atts\_string\_rewrite.c}

*** Tests successful!

\section{Test tst\_attsperf.c}

Too long to run!

\section{Test tst\_bug324.c}

Sorry! Unexpected result, ../../nc\_test4/tst\_bug324.c, line: 71

\section{Test tst\_camrun.c}

tst\_camrun: /home/lucy/esiwace/esdm/src/esdm-datatypes.c:959: esdmI\_dataset\_metadata\_create: Assertion `d->dataspace->size != ((void *)0)' failed.

\section{Test tst\_chunks2.c}

ESDM does not support compression from NetCDF!

Sorry! Unexpected result, ../../nc\_test4/tst\_chunks2.c, line: 106

\section{Test tst\_chunks3.c}

ESDM does not support compression from NetCDF!

Sorry! Unexpected result, ../../nc\_test4/tst\_chunks3.c, line: 284 - NetCDF: Invalid argument

\section{Test tst\_chunks.c}

ESDM does not support compression from NetCDF!

Sorry! Unexpected result, ../../nc\_test4/tst\_chunks.c, line: 49

\section{Test tst\_compounds2.c}

ESDM does not support compound datatypes from NetCDF!

Sorry! Unexpected result, ../../nc\_test4/tst\_compounds2.c, line: 68

\section{Test tst\_compounds3.c}

ESDM does not support compound datatypes from NetCDF!

Sorry! Unexpected result, ../../nc\_test4/tst\_compounds3.c, line: 78

\section{Test tst\_converts2.c}

tst\_converts2: /home/lucy/esiwace/esdm/src/hypercube.c:62: esdmI\_hypercube\_make: Assertion `offset' failed.

\section{Test tst\_converts.c}

Sorry! Unexpected result, ../../nc\_test4/tst\_converts.c, line: 147

2 failures

7 errors detected! Sorry!

\section{Test tst\_coords2.c}

ESDM does not support groups from NetCDF!

Sorry! Unexpected result, ../../nc\_test4/tst\_coords2.c, line: 88

\section{Test tst\_coords3.c}

ESDM does not support groups from NetCDF!

Sorry! Unexpected result, ../../nc\_test4/tst\_coords3.c, line: 126

Sorry! Unexpected result, ../../nc\_test4/tst\_coords3.c, line: 268

\section{Test tst\_coords.c}

ESDM does not support groups from NetCDF!

Sorry! Unexpected result, ../../nc\_test4/tst\_coords.c, line: 76

\section{Test tst\_create\_files.c}

ESDM does not support groups from NetCDF!

\section{Test tst\_dims.c}

ESDM does not support groups from NetCDF!

Sorry! Unexpected result, ../../nc\_test4/tst\_dims.c, line: 61

\section{Test tst\_dims2.c}

Sorry! Unexpected result, ../../nc\_test4/tst\_dims2.c, line: 59

\section{Test tst\_dims3.c}

Sorry! Unexpected result, ../../nc\_test4/tst\_dims3.c, line: 52

\section{Test tst\_elatefill.c}

line 41 expecting NC\_ELATEFILL but got 0

\section{Test tst\_empty\_vlen\_unlim.c}

ESDM does not support user defined datatypes from NetCDF!

\section{Test tst\_endian\_fill.c}

NetCDF Feature not supported with ESDM!

Sorry! Unexpected result, ../../nc\_test4/tst\_endian\_fill.c, line: 35

\section{Test tst\_enums.c}

ESDM does not support user defined datatypes from NetCDF!

Sorry! Unexpected result, ../../nc\_test4/tst\_enums.c, line: 47

\section{Test tst\_files3.c}

ESDM does not support compression from NetCDF!

Sorry! Unexpected result, ../../nc\_test4/tst\_files3.c, line: 88

Sorry! Unexpected result, ../../nc\_test4/tst\_files3.c, line: 206

\section{Test tst\_files4.c}

ESDM does not support groups from NetCDF!

Sorry! Unexpected result, ../../nc\_test4/tst\_files4.c, line: 66

\section{Test tst\_files5.c}

*** Tests successful!

\section{Test tst\_files6.c}

*** testing HDF5 file with circular group structure...[ESDM NC] called ESDM\_open:303 tst\_files6.h5 65536 0 tst\_files6.h5

Sorry! Unexpected result, ../../nc\_test4/tst\_files6.c, line: 86

\section{Test tst\_files.c}

Sorry! Unexpected result, ../../nc\_test4/tst\_files.c, line: 131

\section{Test tst\_fill\_attr\_vanish.c}

Sorry! Expecting NC\_ELATEFILL but got No error, at file ../../nc\_test4/tst\_fill\_attr\_vanish.c line: 95

\section{Test tst\_fillbug.c}

Sorry! Unexpected result, ../../nc\_test4/tst\_fillbug.c, line: 64

\section{Test tst\_fills2.c}

Sorry! Unexpected result, ../../nc\_test4/tst\_fills2.c, line: 48

\section{Test tst\_fills.c}

Sorry! Unexpected result, ../../nc\_test4/tst\_fills.c, line: 59

\section{Test tst\_filterparser.c}

SUCCESS!!

\section{Test tst\_grps2.c}

ESDM does not support groups from NetCDF!

Sorry! Unexpected result, ../../nc\_test4/tst\_grps2.c, line: 56

\section{Test tst\_grps.c}

ESDM does not support groups from NetCDF!

Sorry! Unexpected result, ../../nc\_test4/tst\_grps.c, line: 51

\section{Test tst\_h5\_endians.c}

NetCDF Feature not supported with ESDM!

\section{Test tst\_hdf5\_file\_compat.c}

Sorry! Unexpected result, ../../nc\_test4/tst\_hdf5\_file\_compat.c, line: 42

\section{Test tst\_h\_refs.c}

Sorry! Unexpected result, ../../nc\_test4/tst\_h\_refs.c, line: 85

\section{Test tst\_h\_scalar.c}

Sorry! Unexpected result, ../../nc\_test4/tst\_h\_scalar.c, line: 272

\section{Test tst\_h\_strbug.c}

Sorry! Unexpected result, ../../nc\_test4/tst\_h\_strbug.c, line: 96

\section{Test tst\_interops5.c}

Sorry! Unexpected result, ../../nc\_test4/tst\_interops5.c, line: 164

\section{Test tst\_interops6.c}

Sorry! Unexpected result, ../../nc\_test4/tst\_interops6.c, line: 159

\section{Test tst\_interops.c}

Sorry! Unexpected result, ../../nc\_test4/tst\_interops.c, line: 126

\section{Test tst\_large2.c}

Not tested yet.

\section{Test tst\_large.c}

WARN ESDM\_set\_fill():503 NOT IMPLEMENTED

\section{Test tst\_mem.c}

*** Tests successful!

\section{Test tst\_mode.c}

ESDM does not support compression from NetCDF!

Sorry! Unexpected result, ../../nc\_test4/tst\_mode.c, line: 27

\section{Test tst\_mpi\_parallel.c}

*** Tests successful!

\section{Test tst\_opaques.c}

ESDM does not support user defined datatypes from NetCDF!

Sorry! Unexpected result, ../../nc\_test4/tst\_opaques.c, line: 49

\section{Test tst\_parallel.c}

WARN ESDM\_var\_par\_access():520 NOT IMPLEMENTED

\section{Test tst\_put\_vars.c}

*** SUCCESS writing example file tst\_put\_vars.nc!

\section{Test tst\_rehash.c}

Tests successful!

\section{Test tst\_rename2.c}

*** Tests successful!

\section{Test tst\_rename.c}

ESDM does not support groups from NetCDF!

Sorry! Unexpected result, ../../nc\_test4/tst\_rename.c, line: 509

\section{Test tst\_simplerw\_coll\_r.c}

WARN ESDM\_var\_par\_access():520 NOT IMPLEMENTED

Sorry! Unexpected result, ../../nc\_test4/tst\_simplerw\_coll\_r.c, line: 329

\section{Test tst\_strings2.c}

*** Tests successful!

\section{Test tst\_strings.c}

Sorry! Unexpected result, ../../nc\_test4/tst\_strings.c, line: 122

\section{Test tst\_sync.c}

*** Tests successful!

\section{Test tst\_types.c}

ESDM does not support user defined datatypes from NetCDF!

Sorry! Unexpected result, ../../nc\_test4/tst\_types.c, line: 106

\section{Test tst\_udf.c}

Sorry! Unexpected result, ../../nc\_test4/tst\_udf.c, line: 233

\section{Test tst\_unlim\_vars.c}

Sorry! Unexpected result, ../../nc\_test4/tst\_unlim\_vars.c, line: 70

\section{Test tst\_utf8.c}

Sorry! Unexpected result, ../../nc\_test4/tst\_utf8.c, line: 189

\section{Test tst\_v2.c}

*** Tests successful!

\section{Test tst\_varms.c}

*** Tests successful!

\section{Test tst\_vars2.c}

ESDM does not support groups from NetCDF!

Sorry! Unexpected result, ../../nc\_test4/tst\_vars2.c, line: 100

\section{Test tst\_vars3.c}

ESDM does not support groups from NetCDF!

Sorry! Unexpected result, ../../nc\_test4/tst\_vars3.c, line: 114

\section{Test tst\_vars4.c}

ESDM does not support compression from NetCDF!

Sorry! Unexpected result, ../../nc\_test4/tst\_vars4.c, line: 74

\section{Test tst\_vars.c}

ESDM does not support groups from NetCDF!

Sorry! Unexpected result, ../../nc\_test4/tst\_vars.c, line: 336

\section{Test tst\_vl.c}

ESDM does not support user defined datatypes from NetCDF!

Sorry! Unexpected result, ../../nc\_test4/tst\_vl.c, line: 55

\section{Test t\_type.c}

*** Tests successful!

\clearpage

\begin{table}[H]
\centering
\begin{tabular}{|m{2cm}|m{3cm}|m{3cm}|m{3cm}|m{3cm}|m{2cm}|}
\hline
Test & Test       & Steps   & Expected  & Actual & Status\\
Name & Objective  &         & Output    & Output &               \\ \hline \hline
h5testszip.c   &   &   &   &   &   \\ \hline
cdm\_sea\_soundings.c   &   &   &   &   &   \\ \hline
test\_szip.c   &   &   &   &   &   \\ \hline
tst\_atts1.c   &   &   &   &   &   \\ \hline
tst\_atts2.c   &   &   &   &   &   \\ \hline
tst\_atts3.c   &   &   &   &   &   \\ \hline
tst\_atts.c   &   &   &   &   &   \\ \hline
tst\_atts\_string\_rewrite.c   &   &   &   &   &   \\ \hline
tst\_attsperf.c   &   &   &   &   &   \\ \hline
tst\_bug324.c   &   &   &   &   &   \\ \hline
tst\_camrun.c   &   &   &   &   &   \\ \hline
tst\_chunks2.c   &   &   &   &   &   \\ \hline
tst\_chunks3.c   &   &   &   &   &   \\ \hline
tst\_chunks.c   &   &   &   &   &   \\ \hline
tst\_compounds2.c   &   &   &   &   &   \\ \hline
tst\_compounds3.c   &   &   &   &   &   \\ \hline
tst\_converts2.c   &   &   &   &   &   \\ \hline
tst\_converts.c   &   &   &   &   &   \\ \hline
tst\_coords2.c   &   &   &   &   &   \\ \hline
tst\_coords3.c   &   &   &   &   &   \\ \hline
tst\_coords.c   &   &   &   &   &   \\ \hline
tst\_create\_files.c   &   &   &   &   &   \\ \hline
tst\_dims2.c   &   &   &   &   &   \\ \hline
tst\_dims3.c   &   &   &   &   &   \\ \hline
tst\_elatefill.c   &   &   &   &   &   \\ \hline
tst\_empty\_vlen\_unlim.c   &   &   &   &   &   \\ \hline
tst\_endian\_fill.c   &   &   &   &   &   \\ \hline
tst\_enums.c   &   &   &   &   &   \\ \hline
tst\_files3.c   &   &   &   &   &   \\ \hline
tst\_files5.c   &   &   &   &   &   \\ \hline
tst\_files4.c   &   &   &   &   &   \\ \hline
tst\_files6.c   &   &   &   &   &   \\ \hline
tst\_files.c   &   &   &   &   &   \\ \hline
tst\_fill\_attr\_vanish.c   &   &   &   &   &   \\ \hline
tst\_fillbug.c   &   &   &   &   &   \\ \hline
tst\_fills2.c   &   &   &   &   &   \\ \hline
tst\_fills.c   &   &   &   &   &   \\ \hline
tst\_filterparser.c   &   &   &   &   &   \\ \hline
tst\_grps2.c   &   &   &   &   &   \\ \hline
tst\_grps.c   &   &   &   &   &   \\ \hline
tst\_h5\_endians.c   &   &   &   &   &   \\ \hline
tst\_hdf5\_file\_compat.c   &   &   &   &   &   \\ \hline
tst\_h\_refs.c   &   &   &   &   &   \\ \hline
tst\_h\_scalar.c   &   &   &   &   &   \\ \hline
tst\_h\_strbug.c   &   &   &   &   &   \\ \hline
tst\_interops5.c   &   &   &   &   &   \\ \hline
tst\_interops6.c   &   &   &   &   &   \\ \hline
tst\_interops.c   &   &   &   &   &   \\ \hline
tst\_large2.c   &   &   &   &   &   \\ \hline
tst\_large.c   &   &   &   &   &   \\ \hline
\hline
\end{tabular}
\caption{Test Case Report: ESDM and NetCDF compatibility}
\end{table}

\clearpage

\begin{table}[H]
\centering
\begin{tabular}{|l|c|c|c|c|c|}
\hline
Filename & Compatible & Almost      & Not Compatible  & Almost        & Incompatible \\
         &            & Compatible  & Yet             & Incompatible  &               \\ \hline \hline
tst\_mem.c   &   &   &   &   &   \\ \hline
tst\_mode.c   &   &   &   &   &   \\ \hline
tst\_mpi\_parallel.c   &   &   &   &   &   \\ \hline
tst\_opaques.c   &   &   &   &   &   \\ \hline
tst\_parallel.c   &   &   &   &   &   \\ \hline
tst\_put\_vars.c   &   &   &   &   &   \\ \hline
tst\_rehash.c   &   &   &   &   &   \\ \hline
tst\_rename2.c   &   &   &   &   &   \\ \hline
tst\_rename.c   &   &   &   &   &   \\ \hline
tst\_simplerw\_coll\_r.c   &   &   &   &   &   \\ \hline
tst\_strings2.c   &   &   &   &   &   \\ \hline
tst\_strings.c   &   &   &   &   &   \\ \hline
tst\_sync.c   &   &   &   &   &   \\ \hline
tst\_types.c   &   &   &   &   &   \\ \hline
tst\_udf.c   &   &   &   &   &   \\ \hline
tst\_unlim\_vars.c   &   &   &   &   &   \\ \hline
tst\_utf8.c   &   &   &   &   &   \\ \hline
tst\_v2.c   &   &   &   &   &   \\ \hline
tst\_varms.c   &   &   &   &   &   \\ \hline
tst\_vars2.c   &   &   &   &   &   \\ \hline
tst\_vars3.c   &   &   &   &   &   \\ \hline
tst\_vars4.c   &   &   &   &   &   \\ \hline
tst\_vars.c   &   &   &   &   &   \\ \hline
tst\_vl.c   &   &   &   &   &   \\ \hline
t\_type.c   &  &   &   &   &   \\ \hline
\hline
\end{tabular}
\caption{Test Case Report: ESDM and NetCDF compatibility}
\end{table}





\begin{table}[H]
\centering
\begin{tabular}{|l|c|c|c|c|c|}
\hline
Filename & Compatible & Almost      & Not Compatible  & Almost        & Incompatible \\
         &            & Compatible  & Yet             & Incompatible  &               \\ \hline \hline
cdm\_sea\_soundings.c   &   &   &   &   &  $\checkmark$ \\ \hline
test\_szip.c   &   &   &   &   & $\checkmark$  \\ \hline
tst\_atts1.c   &   &   &   &   &   \\ \hline
tst\_atts2.c   &   &   &   &   & $\checkmark$  \\ \hline
tst\_atts3.c   &   &   &   &   &   \\ \hline
tst\_atts.c   &   &   &   &   &   \\ \hline
tst\_attsperf.c   &   &   &   &   &   \\ \hline
tst\_bug324.c   &   &   &   &   &   \\ \hline
tst\_camrun.c   &   &   &   &   &   \\ \hline
tst\_chunks2.c   &   &   &   &   &   \\ \hline
tst\_chunks3.c   &   &   &   &   &   \\ \hline
tst\_chunks.c   &   &   &   &   &   \\ \hline
tst\_compounds2.c   &   &   &   &   &   \\ \hline
tst\_compounds3.c   &   &   &   &   &   \\ \hline
tst\_converts2.c   &   &   &   &   &   \\ \hline
tst\_converts.c   &   &   &   &   &   \\ \hline
tst\_coords2.c   &   &   &   &   &   \\ \hline
tst\_coords3.c   &   &   &   &   &   \\ \hline
tst\_coords.c   &   &   &   &   &   \\ \hline
tst\_create\_files.c   &   &   &   &   &   \\ \hline
tst\_dims2.c   &   &   &   &   &   \\ \hline
tst\_dims3.c   &   &   &   &   &   \\ \hline
tst\_empty\_vlen\_unlim.c   &   &   &   &   &   \\ \hline
tst\_endian\_fill.c   &   &   &   &   &   \\ \hline
tst\_enums.c   &   &   &   &   &   \\ \hline
tst\_files4.c   &   &   &   &   &   \\ \hline
tst\_files6.c   &   &   &   &   &   \\ \hline
tst\_files.c   &   &   &   &   &   \\ \hline
tst\_fill\_attr\_vanish.c   &   &   &   &   &   \\ \hline
tst\_fillbug.c   &   &   &   &   &   \\ \hline
tst\_fills2.c   &   &   &   &   &   \\ \hline
tst\_fills.c   &   &   &   &   &   \\ \hline
tst\_grps2.c   &   &   &   &   &   \\ \hline
tst\_grps.c   &   &   &   &   &   \\ \hline
tst\_h5\_endians.c   &   &   &   &   &   \\ \hline
tst\_hdf5\_file\_compat.c   &   &   &   &   &   \\ \hline
tst\_h\_refs.c   &   &   &   &   &   \\ \hline
tst\_h\_scalar.c   &   &   &   &   &   \\ \hline
tst\_h\_strbug.c   &   &   &   &   &   \\ \hline
tst\_interops5.c   &   &   &   &   &   \\ \hline
tst\_interops6.c   &   &   &   &   &   \\ \hline
tst\_interops.c   &   &   &   &   &   \\ \hline
tst\_large2.c   &   &   &   &   &   \\ \hline
tst\_large.c   &   &   &   &   &   \\ \hline
\hline
\end{tabular}
\caption{}
\end{table}

\clearpage

\begin{table}[H]
\centering
\begin{tabular}{|l|c|c|c|c|c|}
\hline
Filename & Compatible & Almost      & Not Compatible  & Almost        & Incompatible \\
         &            & Compatible  & Yet             & Incompatible  &               \\ \hline \hline
tst\_mem.c   &   &   &   &   &   \\ \hline
tst\_mode.c   &   &   &   &   &   \\ \hline
tst\_opaques.c   &   &   &   &   &   \\ \hline
tst\_parallel.c   &   &   &   &   &   \\ \hline
tst\_put\_vars.c   &   &   &   &   &   \\ \hline
tst\_rename2.c   &   &   &   &   &   \\ \hline
tst\_rename.c   &   &   &   &   &   \\ \hline
tst\_simplerw\_coll\_r.c   &   &   &   &   &   \\ \hline
tst\_strings2.c   &   &   &   &   &   \\ \hline
tst\_strings.c   &   &   &   &   &   \\ \hline
tst\_sync.c   &   &   &   &   &   \\ \hline
tst\_types.c   &   &   &   &   &   \\ \hline
tst\_udf.c   &   &   &   &   &   \\ \hline
tst\_unlim\_vars.c   &   &   &   &   &   \\ \hline
tst\_utf8.c   &   &   &   &   &   \\ \hline
tst\_v2.c   &   &   &   &   &   \\ \hline
tst\_varms.c   &   &   &   &   &   \\ \hline
tst\_vars2.c   &   &   &   &   &   \\ \hline
tst\_vars3.c   &   &   &   &   &   \\ \hline
tst\_vars4.c   &   &   &   &   &   \\ \hline
tst\_vars.c   &   &   &   &   &   \\ \hline
tst\_vl.c   &   &   &   &   &   \\ \hline
h5testszip.c   & $\checkmark$  &   &   &   &   \\ \hline
tst\_atts\_string\_rewrite.c   & $\checkmark$  &   &   &   &   \\ \hline
tst\_elatefill.c   & $\checkmark$  &   &   &   &   \\ \hline
tst\_files3.c   & $\checkmark$  &   &   &   &   \\ \hline
tst\_files5.c   & $\checkmark$  &   &   &   &   \\ \hline
tst\_filterparser.c   & $\checkmark$  &   &   &   &   \\ \hline
tst\_mpi\_parallel.c   & $\checkmark$  &   &   &   &   \\ \hline
tst\_rehash.c   & $\checkmark$  &   &   &   &   \\ \hline
t\_type.c   & $\checkmark$ &   &   &   &   \\ \hline
\hline
\end{tabular}
\caption{}
\end{table}

\begin{table}[H]
\centering
\begin{tabular}{|l|l|}
\hline
Filename & Justification \\ \hline \hline
cdm\_sea\_soundings.c   & ESDM does not support compound datatypes from NetCDF!          \\ \hline
test\_szip.c   &  ESDM does not support compression from NetCDF!         \\ \hline
tst\_atts1.c   &           \\ \hline
tst\_atts2.c   &  ESDM does not support compound datatypes from NetCDF!         \\ \hline
tst\_atts3.c   &           \\ \hline
tst\_atts.c   &           \\ \hline
tst\_attsperf.c   &  Too long to test now.         \\ \hline
tst\_bug324.c   &  ESDM does not support classic format from NetCDF!         \\ \hline
tst\_camrun.c   &           \\ \hline
tst\_chunks2.c   &  ESDM does not support compression from NetCDF!         \\ \hline
tst\_chunks3.c   & ESDM does not support compression from NetCDF!       \\ \hline
tst\_chunks.c   &  ESDM does not support compression from NetCDF!       \\ \hline
tst\_compounds2.c   &  ESDM does not support compound datatypes from NetCDF!         \\ \hline
tst\_compounds3.c   &  ESDM does not support compound datatypes from NetCDF!         \\ \hline
tst\_converts2.c   &           \\ \hline
tst\_converts.c   &           \\ \hline
tst\_coords2.c   &   ESDM does not support groups from NetCDF!       \\ \hline
tst\_coords3.c   &  ESDM does not support groups from NetCDF!         \\ \hline
tst\_coords.c   &  ESDM does not support groups from NetCDF!         \\ \hline
tst\_create\_files.c   &   ESDM does not support groups from NetCDF!        \\ \hline
tst\_dims2.c   & ESDM does not preserve the ID of the dimensions once it is closed!       \\ \hline
tst\_dims3.c   & ESDM does not support groups from NetCDF!      \\ \hline
tst\_empty\_vlen\_unlim.c   &  ESDM does not support user-defined datatypes from NetCDF!    \\ \hline
tst\_endian\_fill.c   &    ESDM does not support endianness from NetCDF! \\ \hline
tst\_enums.c   &   ESDM does not support user-defined datatypes from NetCDF!   \\ \hline
tst\_files4.c   &   ESDM does not support groups from NetCDF!    \\ \hline
tst\_files6.c   &  ESDM does not support HDF5 file with circular group structure!    \\ \hline
tst\_files.c   &       \\ \hline
tst\_fill\_attr\_vanish.c   &   WARN ESDM\_set\_fill():370 NOT IMPLEMENTED    \\ \hline
tst\_fillbug.c   &  WARN\_NOT\_IMPLEMENTED     \\ \hline
tst\_fills2.c   &   WARN\_NOT\_IMPLEMENTED    \\ \hline
tst\_fills.c   &    WARN\_NOT\_IMPLEMENTED   \\ \hline
tst\_grps2.c   &   ESDM does not support groups from NetCDF!    \\ \hline
tst\_grps.c   &    ESDM does not support groups from NetCDF!   \\ \hline
tst\_h5\_endians.c   &   ESDM does not support endianness from NetCDF!  \\ \hline
tst\_hdf5\_file\_compat.c   &  ESDM does not support HDF5 format!     \\ \hline
tst\_h\_refs.c   &   ESDM does not support HDF5 format!    \\ \hline
tst\_h\_scalar.c   &  ESDM does not support HDF5 format!    \\ \hline
tst\_h\_strbug.c   &  ESDM does not support HDF5 format!     \\ \hline
tst\_interops5.c   &   ESDM does not support HDF5 format!    \\ \hline
tst\_interops6.c   &   ESDM does not support HDF5 format!    \\ \hline
tst\_interops.c   &   ESDM does not support HDF5 format!    \\ \hline
tst\_large2.c   &   Broke my computer    \\ \hline
tst\_large.c   &   WARN ESDM\_set\_fill():526 NOT IMPLEMENTED (Tests successful!)   \\ \hline
\hline
\end{tabular}
\caption{}
\end{table}

\clearpage

\begin{table}[H]
\centering
\begin{tabular}{|l|l|}
\hline
Filename & Justification \\ \hline \hline
tst\_mem.c   &    Tests successful!   \\ \hline
tst\_mode.c   &   ESDM does not support compression from NetCDF! (Tests successful!)    \\ \hline
tst\_opaques.c   &  ESDM does not support user-defined datatypes from NetCDF!     \\ \hline
tst\_parallel.c   &   Not tested yet.    \\ \hline
tst\_put\_vars.c   &   SUCCESS writing example file!    \\ \hline
tst\_rename2.c   &  ESDM does not support NC\_NAT from NetCDF!     \\ \hline
tst\_rename.c   &   It works until get to a function requiring groups!  \\ \hline
tst\_simplerw\_coll\_r.c   &   ESDM does not support collective access of metadata with HDF5!  \\ \hline
tst\_strings2.c   &   Tests successful!    \\ \hline
tst\_strings.c   &  ESDM does not support NC\_STRING from NetCDF!     \\ \hline
tst\_sync.c   &  It does not work just because ESDM does not use the NC\_EINDEFINE flag!  \\ \hline
tst\_types.c   &  ESDM does not support user-defined datatypes from NetCDF!     \\ \hline
tst\_udf.c   &   ESDM does not support user-defined formats from NetCDF!   \\ \hline
tst\_unlim\_vars.c   &   Soometimes works, sometimes doesn't work!    \\ \hline
tst\_utf8.c   &   ESDM does not support Unicode names encoded with UTF-8!  \\ \hline
tst\_v2.c   &    Tests successful!   \\ \hline
tst\_varms.c   &   ESDM does not support mapped var operations!  \\ \hline
tst\_vars2.c   &  ESDM does not support NC\_NAT from NetCDF!  \\ \hline
tst\_vars3.c   &       \\ \hline
tst\_vars4.c   &  ESDM does not support compression from NetCDF!     \\ \hline
tst\_vars.c   &    ESDM does not support groups from NetCDF!   \\ \hline
tst\_vl.c   &   ESDM does not support user-defined datatypes from NetCDF!    \\ \hline
h5testszip.c   & PASS   \\ \hline
tst\_atts\_string\_rewrite.c   & Tests successful!  \\ \hline
tst\_elatefill.c   & line 41 expecting NC\_ELATEFILL but got 0   \\ \hline
tst\_files3.c   & Working ESDM does not support compression from NetCDF!   \\ \hline
tst\_files5.c   & Not working anymore (Tests successful!)  \\ \hline
tst\_filterparser.c   & SUCCESS!!   \\ \hline
tst\_mpi\_parallel.c   & Tests successful!   \\ \hline
tst\_rehash.c   & Tests successful!  \\ \hline
t\_type.c   & Tests successful!   \\ \hline
\hline
\end{tabular}
\caption{Additional comments on ESDM and NETCDF compatibility}
\end{table}

\begin{table}[H]
\centering
\begin{tabular}{|l|c|c|c|c|}
\hline
File & Not Tested & Not Working Build & Not Working Run & Working \\ \hline \hline
bigmeta.c   & $\checkmark$  &   &   &    \\ \hline
openbigmeta.c & $\checkmark$   &   &   &    \\ \hline
bm\_file.c   &  & $\checkmark$  &   &    \\ \hline
bm\_many\_atts.c   &  & $\checkmark$  &   &    \\ \hline
bm\_many\_objs.c   &  & $\checkmark$  &   &    \\ \hline
bm\_netcdf4\_recs.c   &  & $\checkmark$  &   &    \\ \hline
ref\_bzip2.c   &  & $\checkmark$  &   &    \\ \hline
test\_filter.c   &  & $\checkmark$  &   &    \\ \hline
test\_filter\_misc.c   &  & $\checkmark$  &   &    \\ \hline
tst\_ar4\_3d.c   &  & $\checkmark$  &   &    \\ \hline
tst\_ar4\_4d.c   &  & $\checkmark$  &   &    \\ \hline
tst\_ar4.c   &  & $\checkmark$  &   &    \\ \hline
tst\_files2.c   &  & $\checkmark$  &   &    \\ \hline
tst\_h\_many\_atts.c   &  & $\checkmark$  &   &    \\ \hline
tst\_knmi.c   &  & $\checkmark$  &   &    \\ \hline
tst\_put\_vars\_two\_unlim\_dim.c   &  & $\checkmark$  &   &    \\ \hline
tst\_utils.c   &  & $\checkmark$  &   &    \\ \hline
tst\_compounds.c   &  &   &  $\checkmark$ &    \\ \hline
tst\_dims.c   &  &   &  $\checkmark$ &    \\ \hline
tst\_interops4.c   &  &   &  $\checkmark$ &    \\ \hline
tst\_nc4perf.c   &  &   &  $\checkmark$ &    \\ \hline
tst\_parallel3.c   &  &   &  $\checkmark$ &    \\ \hline
tst\_parallel4.c   &  &   &  $\checkmark$ &    \\ \hline
tst\_parallel5.c   &  &   &  $\checkmark$ &    \\ \hline
tst\_xplatform2.c   &  &   &  $\checkmark$ &    \\ \hline
tst\_xplatform.c   &  &   &  $\checkmark$ &    \\ \hline
\hline
\end{tabular}
\caption{List of nc\_test4 files.}
\end{table}

\begin{table}[H]
\centering
\begin{tabular}{|l|c|c|c|c|}
\hline
File & Not Tested & Not Working Build & Not Working Run & Working \\ \hline \hline
renamegroup.c   &  &   &   & $\checkmark$    \\ \hline
test\_szip.c   &  &   &   & $\checkmark$    \\ \hline
tst\_atts1.c   &  &   &   & $\checkmark$    \\ \hline
tst\_atts2.c   &  &   &   & $\checkmark$    \\ \hline
tst\_atts3.c   &  &   &   & $\checkmark$    \\ \hline
tst\_atts.c   &  &   &   & $\checkmark$    \\ \hline
tst\_attsperf.c   &  &   &   & $\checkmark$    \\ \hline
tst\_atts\_string\_rewrite.c   &  &   &   & $\checkmark$    \\ \hline
tst\_bug324.c   &  &   &   & $\checkmark$    \\ \hline
tst\_camrun.c   &  &   &   & $\checkmark$    \\ \hline
tst\_chunks2.c   &  &   &   & $\checkmark$    \\ \hline
tst\_chunks3.c   &  &   &   & $\checkmark$    \\ \hline
tst\_chunks.c   &  &   &   & $\checkmark$    \\ \hline
tst\_compounds2.c   &  &   &   & $\checkmark$    \\ \hline
tst\_compounds3.c   &  &   &   & $\checkmark$    \\ \hline
tst\_converts2.c   &  &   &   & $\checkmark$    \\ \hline
tst\_converts.c   &  &   &   & $\checkmark$    \\ \hline
tst\_coords2.c   &  &   &   & $\checkmark$    \\ \hline
tst\_coords3.c   &  &   &   & $\checkmark$    \\ \hline
tst\_coords.c   &  &   &   & $\checkmark$    \\ \hline
tst\_create\_files.c   &  &   &   & $\checkmark$    \\ \hline
tst\_dims2.c   &  &   &   & $\checkmark$    \\ \hline
tst\_dims3.c   &  &   &   & $\checkmark$    \\ \hline
tst\_elatefill.c   &  &   &   & $\checkmark$    \\ \hline
tst\_empty\_vlen\_unlim.c   &  &   &   & $\checkmark$    \\ \hline
tst\_endian\_fill.c   &  &   &   & $\checkmark$    \\ \hline
tst\_enums.c   &  &   &   & $\checkmark$    \\ \hline
tst\_files3.c   &  &   &   & $\checkmark$    \\ \hline
tst\_files4.c   &  &   &   & $\checkmark$    \\ \hline
tst\_files5.c   &  &   &   & $\checkmark$    \\ \hline
tst\_files6.c   &  &   &   & $\checkmark$    \\ \hline
tst\_files.c   &  &   &   & $\checkmark$    \\ \hline
tst\_fill\_attr\_vanish.c   &  &   &   & $\checkmark$    \\ \hline
tst\_fillbug.c   &  &   &   & $\checkmark$    \\ \hline
tst\_fills2.c   &  &   &   & $\checkmark$    \\ \hline
tst\_fills.c   &  &   &   & $\checkmark$    \\ \hline
tst\_filterparser.c   &  &   &   & $\checkmark$    \\ \hline
tst\_grps2.c   &  &   &   & $\checkmark$    \\ \hline
tst\_grps.c   &  &   &   & $\checkmark$    \\ \hline
tst\_h5\_endians.c   &  &   &   & $\checkmark$    \\ \hline
tst\_hdf5\_file\_compat.c   &  &   &   & $\checkmark$    \\ \hline
tst\_h\_refs.c   &  &   &   & $\checkmark$    \\ \hline
tst\_h\_scalar.c   &  &   &   & $\checkmark$    \\ \hline
tst\_h\_strbug.c   &  &   &   & $\checkmark$    \\ \hline
tst\_interops5.c   &  &   &   & $\checkmark$    \\ \hline
tst\_interops6.c   &  &   &   & $\checkmark$    \\ \hline
tst\_interops.c   &  &   &   & $\checkmark$    \\ \hline
tst\_large2.c   &  &   &   & $\checkmark$    \\ \hline
tst\_large.c   &  &   &   & $\checkmark$    \\ \hline
tst\_mem.c   &  &   &   & $\checkmark$    \\ \hline
\hline
\end{tabular}
\caption{List of nc\_test4 files.}
\end{table}

\begin{table}[H]
\centering
\begin{tabular}{|l|c|c|c|c|}
\hline
File & Not Tested & Not Working Build & Not Working Run & Working \\ \hline \hline
tst\_mode.c   &  &   &   & $\checkmark$    \\ \hline
tst\_mpi\_parallel.c   &  &   &   & $\checkmark$    \\ \hline
tst\_opaques.c   &  &   &   & $\checkmark$    \\ \hline
tst\_parallel.c   &  &   &   & $\checkmark$    \\ \hline
tst\_put\_vars.c   &  &   &   & $\checkmark$    \\ \hline
tst\_rehash.c   &  &   &   & $\checkmark$    \\ \hline
tst\_rename2.c   &  &   &   & $\checkmark$    \\ \hline
tst\_rename.c   &  &   &   & $\checkmark$    \\ \hline
tst\_simplerw\_coll\_r.c   &  &   &   & $\checkmark$    \\ \hline
tst\_strings2.c   &  &   &   & $\checkmark$    \\ \hline
tst\_strings.c   &  &   &   & $\checkmark$    \\ \hline
tst\_sync.c   &  &   &   & $\checkmark$    \\ \hline
tst\_types.c   &  &   &   & $\checkmark$    \\ \hline
tst\_udf.c   &  &   &   & $\checkmark$    \\ \hline
tst\_unlim\_vars.c   &  &   &   & $\checkmark$    \\ \hline
tst\_utf8.c   &  &   &   & $\checkmark$    \\ \hline
tst\_v2.c   &  &   &   & $\checkmark$    \\ \hline
tst\_varms.c   &  &   &   & $\checkmark$    \\ \hline
tst\_vars2.c   &  &   &   & $\checkmark$    \\ \hline
tst\_vars3.c   &  &   &   & $\checkmark$    \\ \hline
tst\_vars4.c   &  &   &   & $\checkmark$    \\ \hline
tst\_vars.c   &  &   &   & $\checkmark$    \\ \hline
tst\_vl.c   &  &   &   & $\checkmark$    \\ \hline
t\_type.c   &  &   &   & $\checkmark$    \\ \hline
\hline
\end{tabular}
\caption{List of nc\_test4 files.}
\end{table}

\clearpage

\begin{table}[H]
\centering
\begin{tabular}{|l|c|l|l|}
\hline
NetCDF TYPE & Number & ESDM Type & ESDM Representation \\ \hline \hline
NC\_BYTE       &  1   & SMD\_DTYPE\_INT8     & int8\_t    \\ \hline
NC\_UBYTE      &  7   & SMD\_DTYPE\_UINT8    & uint8\_t    \\ \hline
NC\_CHAR       &  2   & SMD\_DTYPE\_CHAR     & char    \\ \hline
NC\_SHORT      &  3   & SMD\_DTYPE\_INT16    & int16\_t    \\ \hline
NC\_USHORT     &  8   & SMD\_DTYPE\_UINT16   & uint16\_t    \\ \hline
NC\_INT        &  4   & SMD\_DTYPE\_INT32    & int32\_t    \\ \hline
NC\_LONG       &  4   & SMD\_DTYPE\_INT32    & int32\_t    \\ \hline
NC\_UINT       &  9   & SMD\_DTYPE\_UINT32   & uint32\_t    \\ \hline
NC\_INT64      &  10  & SMD\_DTYPE\_INT64    & int64\_t    \\ \hline
NC\_UINT64     &  5   & SMD\_DTYPE\_UINT64   & uint64\_t    \\ \hline
NC\_FLOAT      &  11  & SMD\_DTYPE\_FLOAT    & 32 bits    \\ \hline
NC\_DOUBLE     &  6   & SMD\_DTYPE\_DOUBLE   & 64 bits    \\ \hline
\hline
\end{tabular}
\caption{Convertion between ESDM and NetCDF4 datatypes -- Datatypes sorted by size.}
\end{table}

\begin{table}[H]
\centering
\begin{tabular}{|l|c|l|l|}
\hline
NetCDF TYPE & Number & ESDM Type & ESDM Representation \\ \hline \hline
NC\_BYTE       &  1   & SMD\_DTYPE\_INT8     & int8\_t    \\ \hline
NC\_CHAR       &  2   & SMD\_DTYPE\_CHAR     & char    \\ \hline
NC\_SHORT      &  3   & SMD\_DTYPE\_INT16    & int16\_t    \\ \hline
NC\_INT        &  4   & SMD\_DTYPE\_INT32    & int32\_t    \\ \hline
NC\_LONG       &  4   & SMD\_DTYPE\_INT32    & int32\_t    \\ \hline
NC\_UINT64     &  5   & SMD\_DTYPE\_UINT64   & uint64\_t    \\ \hline
NC\_DOUBLE     &  6   & SMD\_DTYPE\_DOUBLE   & 64 bits    \\ \hline
NC\_UBYTE      &  7   & SMD\_DTYPE\_UINT8    & uint8\_t    \\ \hline
NC\_USHORT     &  8   & SMD\_DTYPE\_UINT16   & uint16\_t    \\ \hline
NC\_UINT       &  9   & SMD\_DTYPE\_UINT32   & uint32\_t    \\ \hline
NC\_INT64      &  10  & SMD\_DTYPE\_INT64    & int64\_t    \\ \hline
NC\_FLOAT      &  11  & SMD\_DTYPE\_FLOAT    & 32 bits    \\ \hline
\hline
\end{tabular}
\caption{Convertion between ESDM and NetCDF4 datatypes -- Datatypes sorted by NETCDF4 description.}
\end{table}

\begin{table}[H]
\centering
\begin{tabular}{|l|l|l|}
\hline
Functionality & NetCDF Support & ESDM Support \\ \hline \hline

& & \\
& \large{Datatypes} & \\
& & \\ \hline \hline

NC Data Type  &  NC Description  & ESDM Data Type  \\ \hline

NC\_NAT & NAT = Not A Type (c.f. NaN) &     NOT SUPPORTED        \\ \hline
NC\_BYTE & signed 1 byte integer &     SMD\_DTYPE\_INT8        \\ \hline
NC\_CHAR & ISO/ASCII character &      SMD\_DTYPE\_CHAR       \\ \hline
NC\_SHORT & signed 2 byte integer &   SMD\_DTYPE\_INT16          \\ \hline
NC\_INT & signed 4 byte integer &     SMD\_DTYPE\_INT32        \\ \hline
NC\_LONG & deprecated, but required for backward compatibility &    SMD\_DTYPE\_INT32         \\ \hline
NC\_FLOAT & single precision floating point number &   SMD\_DTYPE\_FLOAT           \\ \hline
NC\_DOUBLE & double precision floating point number &   SMD\_DTYPE\_DOUBLE          \\ \hline
NC\_UBYTE & unsigned 1 byte int &     SMD\_DTYPE\_UINT8        \\ \hline
NC\_USHORT & unsigned 2-byte int &    SMD\_DTYPE\_UINT16         \\ \hline
NC\_UINT & unsigned 4-byte int &   SMD\_DTYPE\_UINT32          \\ \hline
NC\_INT64 & signed 8-byte int &    SMD\_DTYPE\_INT64         \\ \hline
NC\_UINT64 & unsigned 8-byte int &    SMD\_DTYPE\_UINT64         \\ \hline
NC\_STRING & string &    SMD\_DTYPE\_STRING         \\ \hline
NC\_VLEN & used internally for vlen types &      NOT SUPPORTED YET       \\ \hline
NC\_OPAQUE & used internally for opaque types &     NOT SUPPORTED YET        \\ \hline
NC\_COMPOUND & used internally for compound types &    NOT SUPPORTED YET         \\ \hline
NC\_ENUM & used internally for enum types &       NOT SUPPORTED YET      \\ \hline \hline

& & \\
& \large{Modes -- Creating a file} & \\
& & \\ \hline \hline

NC\_CLOBBER & Overwrite existing file &  ESDM\_CLOBBER       \\ \hline
NC\_NOCLOBBER & Do not overwrite existing file &  ESDM\_NOCLOBBER       \\ \hline
NC\_SHARE & Limit write caching - netcdf classic files only &  NOT SUPPORTED       \\ \hline
NC\_64BIT\_OFFSET & Create 64-bit offset file &    NOT SUPPORTED     \\ \hline
NC\_64BIT\_DATA  & Create CDF-5 file (alias NC\_CDF5) &   NOT SUPPORTED      \\ \hline
NC\_NETCDF4 & Create netCDF-4/HDF5 file &  NOT SUPPORTED       \\ \hline
NC\_CLASSIC\_MODEL & Enforce netCDF classic mode on netCDF-4/HDF5 files &   NOT SUPPORTED      \\ \hline
NC\_DISKLESS & Store data in memory &    NOT SUPPORTED     \\ \hline
NC\_PERSIST & Force the NC\_DISKLESS data from memory to a file &  NOT SUPPORTED       \\ \hline
\hline

& & \\
& \large{Modes -- Opening a file} & \\
& & \\ \hline \hline

NC\_NOWRITE & Open the dataset with read-only access &  ESDM\_NOWRITE       \\ \hline
NC\_WRITE & Open the dataset with read-write access &  ESDM\_WRITE       \\ \hline
NC\_SHARE & Share updates, limit caching &  NOT SUPPORTED       \\ \hline
NC\_WRITE|NC\_SHARE & Open the dataset with read-write access &    NOT SUPPORTED     \\
 & Share updates, limit caching &    \\ \hline
NC\_DISKLESS & Store data in memory &    NOT SUPPORTED     \\ \hline
NC\_PERSIST & Force the NC\_DISKLESS data from memory to a file &  NOT SUPPORTED       \\ \hline
\hline

%& & \\
%& \large{Modes} & \\
%& & \\ \hline \hline

\end{tabular}
\caption{Functionality Supported by NetCDF and ESDM.}
\end{table}
